Crossing Origins by Crossing Formats

### 2012-11-08 main.tex
Mitigation

% \author{\IEEEauthorblockN{Jonas Magazinius}
% \IEEEauthorblockA{Department of Computer Science\\
% Chalmers University of Technology\\
% Gothenburg, Sweden\\
% jonas.magazinius@chalmers.se}
% \and
% \IEEEauthorblockN{Billy Rios}
% \IEEEauthorblockA{dept. name of organization\\
% name of organization, acronyms acceptable\\
% City, United States of America\\
% Email: name@xyz.com}
% \and
% \IEEEauthorblockN{Andrei Sabelfeld}
% \IEEEauthorblockA{Department of Computer Science\\
% Chalmers University of Technology\\
% Gothenburg, Sweden\\
% andrei@chalmers.se}
% }

@@

\begin{abstract}
  In a heterogeneous system like the web, information is exchanged
  between components in versatile formats. A new breed of attacks is
  on the rise that exploit the mismatch between the expected and
  provided content. \emph{Injection attacks} are becoming increasingly
  more sophisticated by operating across multiple
  languages. \emph{Content repurposing} attacks supply malicious
  payload that appears formatted as benign content.
%
  This paper focuses on the root cause of a large class of attacks:
  \emph{polyglots}. A polyglot is a program that is valid in multiple
  programming languages. Polyglots allow multiple interpretation of
  the content, providing a new space of attack vectors. We
  characterize of what constitutes a dangerous format in the web
  setting and identify particularly dangerous formats, with PDF as the
  prime example. We demonstrate that polyglot-based attacks on the web
  open up for insecure communication across Internet origins. We
  perform a systematic study of PDF-based injection and content
  repurposing attacks. We evaluate the current practice in
  client/server content filtering and PDF readers for polyglot-based
  attacks, and report on vulnerabilities in the top 100 Alexa web sites.
  Our recommendations for protective measures on server side, in 
  browsers, and in PDF readers show how to mitigate the attacks.
\end{abstract}

@@

Bridge to the next session saying that we take these attacks to the
next level.

@@

A polyglot can be used for malicious purposes if there is a difference 
between the expected execution environment and the actual environment 
it is executed in. If the content is verified to be benign in 
In the situation where

@@

@@

This attack has been suggested as a potential way to bypass Content Security 
Policy \ref{required}. 
As E4X is only supported in the SpiderMonkey JavaScript engine, used in 
Firefox, this limits the exploitability of this example.
While this is an unlikely scenario using JavaScript as the injected format, 
section \ref{sec:vuln} will show how this can be achieved in practice.

%\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable PHP-program,captionpos=b]
%<?php
%session_start();
%$_SESSION["secret"] = rand();
%?>
%<html><body>
%Your guess: <?=$_GET["guess"]?>!
%The secret is: <?=$_SESSION["secret"]?>
%</body></html>
%\end{lstlisting}
%\begin{lstlisting}[label=lst:html-js,caption=Vulnerable %PHP-program,captionpos=b]
%<html><body>
%Your guess: </body></html>;x=<html><body>!
%The secret is: 521352342
%</body></html>
%\end{lstlisting}
%\if 0
%$
%\fi

@@

For this attack to be successful certain requirements needs to be 
fulfilled.

\begin{itemize}
	\item The service must accept and serve user-supplied files.
	\item The service must verify the user-supplied polyglot under the 
				assumption that it is in the benign format.
	\item There must exist a way of coercing the polyglot to be 
				interpreted as the malicious format.
\end{itemize}

@@

\subsubsection{The PDF format}

@@

The object-tag is used to embed content in a web page, which requires a plug-in to run. The plug-in is selected based on the MIME-type of the content, but because the server delivering the content might not be able to determine its format, the object tag allows a developer to set the type-attribute to guide the browser in which plug-in to run. When the type attribute is used, the corresponding plug-in is run regardless of which MIME-type the server returns and it is up to the plug-in to respond to and handle the content it is served.

In the case of the Adobe Reader plug-in completely disregards the MIME-type supplied by the server and will attempt to interpret any content as PDF.

@@

the minimal malformed structure that is required for Adobe 
Reader to consider it a PDF.

[anything] \%PDF- [anything] \
[ anything ] [space] trailer [space] << [any name value pair] 
/Root [space] <<[any name value pair] /Pages [space]<< [any name value pair] 
>> [any name value pair] >> [any name value pair] >>

@@

\subsection{Polyglot upload}

@@

Clever filters that adapt their filtering to the context in which 
the user content is included. Basically filters that allow input 
that do not form harmful HTML.

@@

%Baidu.com (allows <>, but escapes /)
%LinkedIn (allows <>, but escapes /)
%Soso (allows <>, but escapes /)
%Youku (vulnerable to traditional XSS)
%Soku (vulnerable to traditional XSS)
%alibaba.com (allows <>, but escapes /)
%about.com (vulnerable to traditional XSS, http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
%sogou.com (potential target http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)

@@

@@

\subsubsection{Polyglot upload}

Serve content from a sandbox domain.

@@

Prevent object-tag type attribute to override content type 
provided by server.

\subsection{Reader}

Stricter parsing of PDF files.

Not render content served with incorrect content type.

@@

>>>>

% \author{\IEEEauthorblockN{Jonas Magazinius} 
% \IEEEauthorblockA{Department ofComputer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\
% jonas.magazinius@chalmers.se} 
% \and 
% \IEEEauthorblockN{Billy Rios} 
% \IEEEauthorblockA{dept. name of organization\\ 
% name of organization, acronyms acceptable\\ 
% City, United States of America\\ 
% Email: name@xyz.com} 
% \and 
% \IEEEauthorblockN{Andrei Sabelfeld} 
% \IEEEauthorblockA{Department of Computer Science\\ 
% Chalmers University of Technology\\ 
% Gothenburg, Sweden\\ 
% andrei@chalmers.se} 
% }

@@

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
\emph{Injection attacks} are becoming increasingly more sophisticated by
operating across multiple languages. \emph{Content repurposing} attacks supply
malicious payload that appears formatted as benign content. 
% 
This paper focuseson the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is aprogram that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. We perform a systematic study of
PDF-based injection and content repurposing attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in PDF
readers show how to mitigate the attacks.
\end{abstract}

@@

Bridge to the next section saying that we take these attacks to the next level.

@@

A polyglot can be used for malicious purposes if there is a difference between
the expected execution environment and the actual environment it is executed in.
If the content is verified to be benign in

  In the situation where

@@

% Browser, plug-in/content handler, target, vulnerability, server

@@

This attack has been suggested as a potential way to bypass Content Security
Policy~\cite{Heyes:CSP}. As E4X is only supported in the SpiderMonkey JavaScript
engine, used in Firefox, this limits the exploitability of this example. While
this is an unlikely scenario using JavaScript as the injected format, section
\ref{sec:vuln} will show how this can be achieved in practice.

@@

For this attack to be successful, certain requirements needs to be fulfilled.
\begin{itemize} 
	\item The service must accept and serve user-supplied files.
	\item The service must verify the user-supplied polyglot under the 
	assumption that it is in the benign format. 
	\item The content is served under the same origin as sensitive user 
	information.
	\item There must exist a way of coercing the polyglot to be interpreted 
	as the malicious format. 
\end{itemize}

@@

\subsection{The PDF format}

@@

The object-tag is used to embed content, which requires a plug-in
to run, in a web page. The plug-in is selected based on the MIME-type of the content, but
because the server delivering the content might not be able to determine its
format, the object tag allows a developer to set the type-attribute to guide the
browser in which plug-in to run. When the type attribute is used, the
corresponding plug-in is run regardless of which MIME-type the server returns
and it is up to the plug-in to respond to and handle the content it is served.

As it turns out, various plug-ins deal with the situation differently. The Chrome browser
built-in PDF reader refuses to render content that was served with an inappropriate 
MIME-type. The Java plug-in used to ignore the MIME-type, but after several 
vulnerabilities were disclosed, this behavior was changed.

In the case of the Adobe Reader plug-in, it completely disregards the MIME-type
supplied by the server and will attempt to interpret any content as PDF. If the 
Chrome browser is configured to use the Adobe Reader plug-in, the behavior will 
be the same as in other browsers and the content will be interpreted as PDF.

@@

the minimal malformed structure that is required for Adobe Reader to consider ita PDF.

\begin{lstlisting}[label=lst:minimal-pdf, caption=HTML / E4X Polyglot]
\%PDF-\
trailer<</Root<</Pages<<>>>>>>
\end{lstlisting}

@@

@@

Clever filters that adapt their filtering to the context in which the user
content is included. Basically filters that allow input that do not form harmfulHTML.

@@

%Baidu.com (allows <>, but escapes /) 
%LinkedIn (allows <>, but escapes /) 
%Soso (allows <>, but escapes /) 
%Youku (vulnerable to traditional XSS) 
%Soku (vulnerable to traditional XSS) 
%alibaba.com (allows <>, but escapes /)
%about.com (vulnerable to traditional XSS,
%http://linux.about.com/sitesearch.htm?q=XSS&SUName=--%3E%3Cimg+src=x+onerror=alert%281%29%3E)
%sogou.com (potential target
%http://www.sogou.com/web?query=%25PDF+%3C%3C+%2F+%3E%3E&_asf=www.sogou.com&_ast=1349689275&w=01019900&p=40040100&sut=11010&sst0=1349689274528)

@@

As a content provider on the Internet today there are precautions that one can 
take to mitigate this class of vulnerabilities. Which precautions to take depend 
on the kind of services provided. The mitigation recommendations for syntax 
injection apply to services that rely on user input, and the content repurposing 
recommendations apply to services that serve user-supplied files.

@@

To prevent PDF syntax injection attack, the task is simpler. As mentioned in Section~\ref{sec:vuln}, there is a limited 
set of characters that are essential to create valid PDF syntax, namely \emph{'$<$', '$>$', and '/'}. Filtering 
user input to remove or encode these characters effectively mitigates the vulnerability.

\subsubsection{Content repurposing}

The current best-practice recommendation from Google~\cite{Google:ContentHosting} 
on hosting user-supplied content, is to serve the content from an origin that is 
completely separate, and isolated from the sensitive services. It also describes how 
Google moved away from sanitizing content , as it was found to be insufficient in 
many cases.

Google uses the domain name \emph{googleusercontent.com} to sandbox all the 
untrusted user files that their various services provide for their customers.

@@

Traditionally, browser vendors have allowed the browser to override the 
MIME-type provided by the server for compatibility reasons. This is a compromise 
to deal with the situation that the server is confused as to what kind of content it is serving. This compromise 
has repeatedly shown to lead to security issues. The affected browser vendors 
could help mitigate this problem by limiting the ways content can be coerced to be 
interpreted as a particular format.

In the case of PDF-based polyglots, the browser could intervene when there is a 
mismatch between the content-type provided by the server and the type attribute 
of the object tag. By acknowledging that there could be a potential security issue in 
interpreting the supplied content in the requested format and alerting the user to this
threat, the vulnerability could be mitigated.

One could argue that the browser is as confused as the originating server as to the 
actual format of the content, and that the issue would be best resolved by the 
corresponding plug-in.

\subsection{Interpreter}

As a general rule of thumb, the interpreter at the very least alert the user if the served 
content-type differs from the expected. A preferred alternative would be to 
not attempt to interpret the content at all. This holds true especially when 
the served content-type is well known and radically different from that which 
the interpreter is designed for.

As for the PDF file format, the underlying design decisions has led to the 
current parsing being very relaxed, even with respect to the specification. 
Making the parsing more strict and enforcing many of the specified requirements 
would greatly reduce the attack surface. It is, however, not a complete 
mitigation approach. Since the PDF format is a container format it is designed to 
embed syntax from other files. Even when parsing strictly according to 
the specification, it would be a simple task to create a PDF-based polyglot.

@@

%\begin{lstlisting}[label=lst:php-sample,caption=Vulnerable
%PHP-program,captionpos=b] 
%<?php %session_start(); %$_SESSION["secret"] = rand(); 
%?> 
%<html><body> 
%Your guess: <?=$_GET["guess"]?>! 
%The secret is: <?=$_SESSION["secret"]?> 
%</body></html> 
%\end{lstlisting}
%\begin{lstlisting}[label=lst:html-js,caption=Vulnerable
%PHP-program,captionpos=b] 
%<html><body> 
%Your guess:</body></html>;x=<html><body>! 
%The secret is: 521352342 
%</body></html>
%\end{lstlisting} 
%\if 0 
%$ 
%\fi
